---
title: "AgriLLM Survey Data"
author: "AgriAGI Research, Zhejiang University"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true             # Enable table of contents
    toc_float: true       # Float the table of contents on the left side
    number_sections: true # Automatically number sections
    theme: cosmo          # Web theme style (options: flatly, journal, readable)
---

```{r setup, include=FALSE}
knitr::opts_chunk $ set(echo = FALSE, warning = FALSE, message = FALSE)

# load required packages
library(readxl)
library(kableExtra)
library(dplyr)
```


# Data overview

This page presents the survey data of Agricultural Large Language Models (AgriLLMs).
Data Source: AgriAGI Research, Zhejiang University
Last Updated: `r file.info("AgriLLM_survey_dat/AgriLLM_survey 20260420.xlsx")$mtime`

# Data preview

Below is a preview of the first 10 rows of the dataset:

```{r}
# dead the Excel file using a relative path pointing to the subfolder
# note: R handles spaces in filenames correctly, but using underscores is recommended for future files
df <- read_excel("AgriLLM_survey_dat/AgriLLM_survey 20260420.xlsx")

# render a visually appealing table using kableExtra
df %>%
  head(10) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```



# Complete dataset

The full survey dataset containing all 4 columns is shown below. A scrollable box is applied for better viewing experience if the dataset is large.

```{r}
# render the complete dataset with a fixed-height scrollable container
df %>%
  kable("html", escape = FALSE) %>%
  kable_styling("striped", full_width = TRUE) %>%
  scroll_box(width = "100%", height = "500px")
```








