---
title: "AgriLLM Survey Data"
author: "AgriAGI Research, Zhejiang University"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true             
    toc_float: true       
    number_sections: true 
    theme: cosmo          
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(readxl)
library(kableExtra)
library(dplyr)
library(ggplot2)
```

# Data Overview

This page presents the survey data of Agricultural Large Language Models (AgriLLMs).

**Credit:**

AgriAGI Research, Zhejiang University

Source code and raw data: https://github.com/AgriAGI-Research/AgriLLM_survey_project

Last Updated: `r file.info("AgriLLM_survey_dat/AgriLLM_survey 20260420.xlsx")$mtime`

**Notes:**

If you spot any mistakes, please contact us via Github issue.

---

# Data preview

Below is a preview of the first 10 rows of the dataset:

```{r}
df <- read_excel("AgriLLM_survey_dat/AgriLLM_survey 20260420.xlsx")

df %>%
  head(10) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# Complete dataset

The full survey dataset is shown below. A scrollable box is applied for better viewing experience.

```{r}
df %>%
  kable("html", escape = FALSE) %>%
  kable_styling("striped", full_width = TRUE) %>%
  scroll_box(width = "100%", height = "500px")
```

---

# Descriptive analysis

## 1. Category distribution

```{r}
url_col <- "访问网址"

url_stats <- df %>%
  mutate(URL_Category = case_when(
    grepl("^https?://", .data[[url_col]], ignore.case = TRUE) ~ "具体访问地址 (URL)",
    grepl("小程序", .data[[url_col]]) ~ "小程序",
    grepl("未明确", .data[[url_col]]) ~ "未明确",
    TRUE ~ "其他"
  )) %>%
  count(URL_Category, name = "Count") %>%
  mutate(Percentage = round(Count / sum(Count) * 100, 1))

url_stats %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## 2. Visualization

```{r, fig.width=8, fig.height=5}
ggplot(url_stats, aes(x = reorder(URL_Category, -Count), y = Count, fill = URL_Category)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = paste0(Count, " (", Percentage, "%)")), 
            vjust = -0.5, size = 4) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Distribution of access URL types",
    x = "Category",
    y = "Count",
    caption = "Data source: AgriLLM Survey"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 15, hjust = 1)
  )
```

## 3. Detailed breakdown

```{r}
df %>%
  mutate(URL_category = case_when(
    grepl("^https?://", .data[[url_col]], ignore.case = TRUE) ~ "具体访问地址",
    grepl("小程序", .data[[url_col]]) ~ "小程序",
    grepl("未明确", .data[[url_col]]) ~ "未明确",
    TRUE ~ "其他"
  )) %>%
  select(1, all_of(url_col), URL_category) %>%  
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# Summary statistics

```{r}
summary_df <- data.frame(
  Metric = c("Total Records", "Records with URL", "Records with 小程序", 
             "Records with 未明确", "Other/Uncategorized"),
  Count = c(
    nrow(df),
    sum(grepl("^https?://", df[[url_col]], ignore.case = TRUE)),
    sum(grepl("小程序", df[[url_col]])),
    sum(grepl("未明确", df[[url_col]])),
    sum(!grepl("^https?://|小程序|未明确", df[[url_col]]))
  )
)

summary_df %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```